---
title: "hw3"
author: "Sai Gugulothu"
date: "2/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question 1
Waiter served 244 parties


```{r}
library("ggplot2")
data(tips, package="reshape2")  #Loading data
tips

numParty <- nrow(tips)
numParty


```

#Question 2
From this we can can see each data type
total_bill, tip are numerical
sex, smoker, day, and time are factors of strings
size is an integer
```{r}
str(tips)
```


# Question 3

```{r}



tips$day <- factor(tips[,"day"], levels = c("Thur","Fri","Sat","Sun"))

ordered_dayz <- order(tips$day)
day <- tips[ordered_dayz, 5]
day

```


#Question 4

```{r}
female5 <- tips[tips$sex == 'Female' & tips$size >= 5,]
female5

```

#Question 5

As you can see from this ggplot, the bigger the bill the better the tip rate in general if you look at the linear regression. The anomalies that I can see from this graph is that people tend to give out a lower tip for higher bills. The other anomaly that the lower the bill, the more percentage of tip a person usually gets.  

```{r}
ggplot(tips, aes(x = total_bill, y = tip)) + geom_point() + ggtitle("Tip vs. Total Bill") + geom_smooth(method='lm',formula=y~x)  + xlab("Total Bill")
```

#Question 6

Average tip is 16.08%

```{r}

tips$tiprate <- tips$tip / tips$total_bill
mean(tips$tiprate) * 100

```

#Question 7



```{r}
tips$time <- factor(tips$time, levels = c("Lunch", "Dinner"))
order_time <- tips[order(tips$time),]



ggplot(order_time,  aes(x=time, y=tiprate)) + geom_boxplot() + labs(x = "Course", y = "Tip Rate") + coord_flip() + ggtitle("Time of Day Tip Rate") 




```


#Question 8
As you can see below, there seems to be a positive correlation. There isnt a distict advantage of a person tipping higher if they were a smoker/non smoker. It also didn't matter what sex they were. 

```{r}

ggplot(tips, aes(x=total_bill, y=tip, shape=smoker, color=sex)) + geom_point() + facet_wrap(~day) + xlab('Total Bill') + ylab('Tip Amount')

```


# Question 9 

Usually, males tip more every single day of the week. 
```{r}
ggplot(tips, aes(x=day, fill=sex)) + geom_bar(position="dodge") + ylab("Number of People") + ggtitle("Relationship Between Day of Week and Gender Paid")
```

